---
title: "J20 by subject analysis"
author: "Iris Oren"
date: "14/06/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r initialisation, include=TRUE, echo = FALSE}
AnimalIDCurrent<-"JF110"
DataFile<-"~/Dropbox/ANALYSIS/J20_EEG_Manuscript/Output/SCPPDataframeAll.csv" #Ouput of J20_EEG_Manuscript.Rmd
SpikesPCAFilenameControl<-"~/Dropbox/ANALYSIS/Neuroarchiver/J20EEG/SpikeDetectionMatthias/JF110/DataJF110/E6_detected_spikes_clustered.txt"
SpikePCAFilenameDrug<-""
ClustersToInclude<-c(0,4)  #Specify which clusters to include based on jupyter notebook classifiy_spikes_and_saveCalcClusters.ipynb
TimeZone<-"Europe/london"
Reference<-"CTX" #Reference electrode location
num_files_to_plot<-4
epoch_loss_threshold<-0.2 #Percentage of total epochs lost for displaying plot
epoch_length<-8  #For calculating number of epochs per file
NDF_length<-3600  #For calculating number of epochs per file


#Load packages
library(lubridate)
library(dplyr)
library(lazyeval) #Needed for using ggplot2 library
library(ggplot2)
library(grid)

#Import data and filter for animal
Dataframe<-read.csv(DataFile)
Dataframe<-filter(Dataframe, AnimalIDVariable==AnimalIDCurrent)
Dataframe$TimeOfDay<-as.POSIXct(Dataframe$TimeOfDay)
```

#`r AnimalIDCurrent`

###Dataloss over time
```{r DatalossOverTime, include=TRUE, echo = FALSE}
DataLossOverTime<-ggplot(Dataframe, aes(x=strptime(TimeOfDay, format = "%Y-%m-%d %H:%M:%S"), y=Loss)) + xlab("Date") + ylab("Loss")
DataLossOverTime<-DataLossOverTime + geom_point() +
  geom_hline(yintercept = 20)
DataLossOverTime
```
```{r LossQuantilesECDF, include = TRUE}
#OPTIONAL: manually select dataframe rows when transmitter was on for quantifying the loss of the transmitter. This is determined from the Loss vs Time plot
TransmitterOffTime<-Dataframe$InitialisedTime[1]
TransmitterOnTime<-Dataframe$InitialisedTime[2]
DataframeOn<-filter(Dataframe, InitialisedTime<TransmitterOffTime | InitialisedTime>TransmitterOnTime)

#OR
#DataframeOn<-Dataframe
############

LossECDF<-ecdf(DataframeOn$Loss)
plot(LossECDF, xlab="Loss %", main="ECDF Loss")
QuantileDivisions<-seq(0, 1, 0.05)
LossQuantiles<-quantile(Dataframe$Loss, QuantileDivisions)
NumberLossIntervals<-length(which(DataframeOn$Loss>20))
LossIntervalPercentage<-NumberLossIntervals/nrow(DataframeOn)*100

```

For periods when the transmitter was on, `r LossIntervalPercentage` intervals had loss <20%


###Filter out loss intervals
Filter out when transmitter was switched off/lossy and artifact intervals using the ExcludeInterval variable
```{r FilterOutLoss, include = TRUE, echo = FALSE}
DataframeNoLoss<-filter(Dataframe, ExcludeInterval==0)
```

###Spike count over time

```{r SpikeCountOverTimeControl, include=TRUE, echo = FALSE}
SpikeCountOverTime<-ggplot(DataframeNoLoss, aes(x=strptime(TimeOfDay, format = "%Y-%m-%d %H:%M:%S"), y=SpikeCount, colour=Treatment)) + xlab("Date") + ylab("Spikes/8s")
SpikeCountOverTime<-SpikeCountOverTime + geom_point()
SpikeCountOverTime




```

Binning SpikeCount by hour

```{r BinnedSpikeCountByHour, include=TRUE, echo=FALSE}
IntervalLength=8  #8s intervals analysed in neuroarchiver
SpikePerSec<-Dataframe$SpikeCount/IntervalLength  #Spike count in interval
BinnedSpikePerSec<-c()
TimeOfBin<-c()
SEMBinnedSpikePerSec<-c()
j<-1
for(i in 0:round(nrow(Dataframe)/450)){
  BinnedSpikePerSec[j]<-mean(SpikePerSec[(i*450)+1:((i+1)*450)], na.rm=TRUE)
  SEMBinnedSpikePerSec[j]<-sd(SpikePerSec[(i*450)+1:((i+1)*450)],na.rm=TRUE)/sqrt(450)
  TimeOfBin[j]<-Dataframe$TimeOfDay[(i+0.5)*450] #Midpoint of bin
  j<-j+1
}
TimeOfBin<-as.POSIXct(TimeOfBin, origin="1970-01-01")
BinnedDataframe<-data.frame(TimeOfBin, BinnedSpikePerSec, SEMBinnedSpikePerSec)

BinnedSpikeCountPlot<-ggplot(BinnedDataframe, aes(x=TimeOfBin, y=BinnedSpikePerSec))
BinnedSpikeCountPlot <- BinnedSpikeCountPlot + 
  geom_point(na.rm=TRUE) +
  xlab("Date") +
  ylab(expression(paste("Mean Spike Rate (s"^{-1}*")"))) +
  xlim(BinnedDataframe$TimeOfBin[1], BinnedDataframe$TimeOfBin[145]) +
  ylim(0,0.03) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) 
 

BinnedSpikeCountPlot


ggsave("/Users/irisoren/Dropbox/Presentations general/LabMeetings/JointLabMeeting0717/JF110BinnedSpikeCount.png")
```

###Polar histogram of IIS from neuroarchiver in control condition
```{r PolarHistogram, include=TRUE, echo = FALSE}
DataframeControl<-filter(DataframeNoLoss, Treatment=="Control")
#Manually make new dataframe for histogram plotting. Intialise
SpikeCountHistDF<-data.frame(SpikeCount=double(), HourBin=integer())
#First get the hour of each interval in the dataframe

#DataframeControl$TimeOfDay<-strptime(DataframeControl$TimeOfDay, "%Y-%m-%d %H:%M:%S")
DataframeControl$TimeOfDay<-as.POSIXct(DataframeControl$TimeOfDay)

DataframeControl$HourOfEvent <- hour(DataframeControl$TimeOfDay)

DataframeSelect<-select(DataframeControl, SpikeCount, HourOfEvent)
for(Hour in 0:23){
  DataframeTemp<-filter(DataframeSelect, HourOfEvent==Hour)
  TotalSpikeCount<-sum(DataframeTemp$SpikeCount)
  Total8sIntervals<-nrow(DataframeTemp)
  TempDF<-data.frame(SpikeCount=TotalSpikeCount/Total8sIntervals*8, HourBin=Hour+0.5)
  SpikeCountHistDF<-rbind(SpikeCountHistDF, TempDF)
}

SpikeCountHistDF$Light<-SpikeCountHistDF$HourBin %in% seq(7.5, 18.5)

SpikeCountHist<-ggplot(SpikeCountHistDF, aes(x=HourBin, y=SpikeCount, fill=Light)) + geom_bar(stat = "identity")
SpikeCountHist <- SpikeCountHist +
            xlab("Hour") +
            ylab("Spikes per second") +
            scale_x_continuous(limits = c(0,24), expand = c(0,0), breaks = seq(0, 23, 2)) +
            scale_fill_grey(labels=c("Off", "On")) +
            coord_polar(start = 0) 
SpikeCountHist
```

###Polar plotting of spikes identified by PCA analysis for control conditions

Here, we use the output from the jupyter notebook for plotting circular plots and calculating phase coupling. This analysis does not take into account the number of intervals recorded/lost
```{r PolarPCAHist, include=TRUE, echo=FALSE}
SpikesPCA<-read.csv(SpikesPCAFilenameControl, header=FALSE, sep=" ")
sps=512
names(SpikesPCA)[1]<-"SampleNumber"
names(SpikesPCA)[2]<-"Cluster"
SpikesPCA$Seconds<-(SpikesPCA$SampleNumber)/sps

#Initialise recording time from start of first data file in processor output file
SpikesPCA$Initialised<-SpikesPCA$Seconds+Dataframe$InitialisedTime[1]

#Convert to time of day and hour
SpikesPCA$TimeOfDay<-as.POSIXct(SpikesPCA$Initialised, tz=TimeZone, origin="1970-01-01")
SpikesPCA$HourOfEvent <- hour(SpikesPCA$TimeOfDay)

#Select clusters of interest
SpikesPCA<-SpikesPCA[which(SpikesPCA$Cluster %in% ClustersToInclude),]

#Add variable for light
SpikesPCA$Light <- SpikesPCA$HourOfEvent %in% seq(7,18)

#Shift hour by 0.5
SpikesPCA$HourOfEventShifted<-SpikesPCA$HourOfEvent+0.5

#Plot
fontsize=12

SpikesPCAHist <- ggplot(SpikesPCA,
                        aes(x = HourOfEventShifted, fill = Light)) +
  geom_histogram(breaks = seq(0,   24), binwidth = 2, colour = "grey") + 
  coord_polar(start = 0) + 
  theme_minimal() + 
  scale_fill_grey(labels=c("Off", "On")) + 
  ylab("Count") + 
  ggtitle("IIS by Time of day") + 
  theme(plot.title = element_text (size = fontsize))+
  theme(axis.title.y=element_text (size = fontsize))+
  theme(axis.text.y =element_text (size = fontsize))+
  theme(axis.text.x =element_text (size = fontsize))+
  scale_x_continuous("", limits = c(0, 24), breaks = seq(0, 24), labels = seq(0,24))

SpikesPCAHist

```

###Theta/delta and spikes in control conditions
For animals with cerebellar reference, we can relate the theta/delta ratio to spikes. 
```{r ThetaOverDeltaRawPlot, include=FALSE, echo=FALSE}
AllNDFs_Control<-as.character(unique(DataframeControl$FileName)) 
if(Reference=="CTX"){
  print("Cortical reference so no subthreshold parameters evaluated")
} else{
fig.cap="Spike count and EEG spectral power in control conditions"
#plotting and saving
require(cowplot)
FontSize=14
num_of_epochs<-NDF_length/epoch_length
i <- 1

while (i <= num_files_to_plot ){
  CurrentNDF<-sample(1:length(AllNDFs_Control), 1)  #Sample one NDF at random from controls NDFs. 
  
  CurrentNDF_FileName<-AllNDFs_Control[CurrentNDF]
  CurrentNDF_DF<-filter(DataframeControl,FileName==CurrentNDF_FileName)
  if (dim(CurrentNDF_DF)[1]>num_of_epochs*(1-epoch_loss_threshold)){
        CurrentNDF_FileName<-AllNDFs_Control[CurrentNDF]
        CurrentNDF_date<-as.Date(CurrentNDF_DF$TimeOfDay[1])  #as.Date rather than date() - not sure why, but date() didn't work in ezknitr
        
        #Plot ThetaMeasure outliers excluded
        TitleString<-paste(CurrentNDF_FileName, " ",CurrentNDF_date," ", "SpikeCount") #,
        SpikeCountPlot<-ggplot()
        SpikeCountPlot<-SpikeCountPlot+
          geom_point(data=CurrentNDF_DF, aes(x=TimeOfDay,y=SpikeCount), color="green")+
          theme_minimal() + 
          ylab("Spike Count per 8s epoch") + 
          ggtitle(TitleString) + 
          theme(axis.title.y=element_text (size = FontSize))+
          theme(axis.text.y =element_text (size = FontSize))+
          theme(axis.text.x =element_blank())+
          theme(axis.title.x=element_blank())
        
        #Plot ThetaOverDelta outliers excluded
        TitleString<-"Theta/Delta"
        #as.character(date(CurrentNDF_DF$TimeOfDay)[1]), "Theta/Delta")
        ThetaOverDeltaPlot<-ggplot()
        ThetaOverDeltaPlot<-ThetaOverDeltaPlot+
          geom_point(data=CurrentNDF_DF, aes(x=TimeOfDay,y=ThetaOverDelta), color="blue")+
          theme_minimal() + 
          ylab("Theta over Delta") + 
          ggtitle(TitleString) + 
          theme(axis.title.y=element_text (size = FontSize))+
          theme(axis.text.y =element_text (size = FontSize))+
          theme(axis.text.x =element_blank())+
          theme(axis.title.x=element_blank())
        
        
        
        #Plot of Theta outliers excluded
        TitleString<-"Theta: 4-12Hz" 
        ThetaPlot<-ggplot()
        ThetaPlot<-ThetaPlot+
          geom_point(data=CurrentNDF_DF, aes(x=TimeOfDay,y=Theta), color="red")+
          theme_minimal() + 
          ylab("Power") + 
          ggtitle(TitleString) + 
          theme(axis.title.y=element_text (size = FontSize))+
          theme(axis.text.y =element_text (size = FontSize))+
          theme(axis.text.x =element_blank())+
          theme(axis.title.x=element_blank())
        
        #Plot delta outliers excluded
        TitleString<-"Delta: 0.1-3.9 Hz"
        DeltaPlot<-ggplot()
        DeltaPlot<-DeltaPlot+
          geom_point(data=CurrentNDF_DF, aes(x=TimeOfDay,y=Delta), color="black")+
          theme_minimal() + 
          ylab("Power") + 
          ggtitle(TitleString) + 
          theme(axis.title.y=element_text (size = FontSize))+
          theme(axis.text.y =element_text (size = FontSize))+
          theme(axis.text.x =element_text (size = FontSize, angle=90))
        
        PlotAll_Control<-plot_grid(
          SpikeCountPlot, 
          ThetaOverDeltaPlot, 
          ThetaPlot, 
          DeltaPlot,
          labels = "AUTO", ncol = 1, align = 'v')
        
        print(PlotAll_Control)
        i<-i+1
  }
} 
  
  
}

```

We plot summary data of theta/delta as a function of spike number
```{r ThetaOverDeltaBySpikeNumber, include = TRUE, echo=FALSE}
if(Reference=="CTX"){
  print("Cortical reference so no subthreshold parameters evaluated")
}else{
  SpikeCountPlot<-ggplot(DataframeControl, aes(x=SpikeCount,
                                               y=ThetaOverDelta))+geom_point()
  SpikeCountPlot
}
```